---
title: "R Notebook"
output: html_notebook
---

# CTT Data Tools

## 1. API

```{r api}
library(celltracktech)
library(DBI)
library(RPostgres)
library(duckdb)

source('functions/data_manager.R')

start <- Sys.time()

###settings###
# my_token <- 'token'
my_token <- "c2ed5f935e9b9d4c2e031f8a96277317b7502d989add5947656dbfbeee7082c5"

db_name <- 'tutorial_db'
myproject <- 'Meadows V2' # this is your project name on your CTT account
# conn <- dbConnect(RPostgres::Postgres(), dbname=db_name)
conn <- DBI::dbConnect(duckdb::duckdb(), dbdir = db_name, read_only = FALSE)
#########
outpath <- "./data"
# get_my_data(my_token, outpath, conn, myproject=myproject)
get_my_data(my_token, outpath, con, myproject=myproject, begin=as.Date("2023-08-01"), end=as.Date("2023-08-02"), filetypes=c("raw", "node_health"))
update_db(conn, outpath, myproject)
dbDisconnect(conn)

#findfiles(outpath, 'directory path where you want your caught files to go')

time_elapse <- Sys.time() - start

print(time_elapse)

```

## 2. Github and Pulling data into R from Local Repo.

## 3. About the Functions

### 3.1 Data Manager

#### 3.1.1 load_data
```{r data_manager}
load_data(directory_name=NULL, starttime=NULL, endtime=NULL, tags=NULL)

```

**Arguments**:

* directory_name: the input folder can contain a miscellany of raw downloaded files from the sensor station (beep data, node health, GPS) all in the same folder or subfolders. Zipped folders need to be unzipped, but compressed files do not (i.e. csv.gz files are just fine as they are).

* starttime: start time in POSIXct

* endtime: end time in POSIXct

* tags: a vector of tag IDs

**Value**
The function will return a nested list where each item corresponds to:

1. beep data

2. node health

3. GPS

Within each list item, there is a list for a data frame and the hardware version. Also a column 'v' has been added to each data frame indicating the hardware version.

### 3.2 Node Health

#### 3.2.1 node_channel_plots

**Description**
This function is the 'engine' behind the export function. You can run it standalone with the following parameters, but you don't have to if your sole goal is to ouput image files.

**Usage**
```{r node_channel_plots}
node_channel_plots(health, freq, ids, lat=NULL, lon=NULL)
```

**Arguments**:

* health: the 2nd list item output by the `load_data()` function
* freq: the time interval for which you want variables to be summarized
* ids: a vector if IDs; the ID is of the format "_"
* lat: latitude (optional to produce day/night shading)
* lon: longitude (optional to produce day/night shading)

**Value**

The output is a nested list, where the top level is each combination of channel and node, and each item is a list of the following plots:

1. battery
2. RSSI
3. number of check-ins
4. scaled number of check-ins as line plot over scaled RSSI
5. box plot of node RSSI
The following only for v2
6. latitude
7. longitude
8. scaled RSSI
9. dispersion

#### 3.2.2 node_plots

**Description**
A set of diagnostic plots per node

**Usage**

```{r node_plots}
node_plots(health, nodes, freq, lat = NULL, lon = NULL)
```

**Arguments**
* health: the 2nd data frame output by the load_data() function
* nodes: list of nodes
* freq: the time interval for which you want variables to be summarized
* lat: latitude
* lon: longitude

**Value**
The output is a nested list for each node, with the following plots for each:

1. RSSI
2. number of check-ins
3. battery
  the following only for v2
4. time mismatches
5. small time mismatches

#### 3.2.3 gps_plots

**Description**
Plots to visualize some GPS data. Only for v2 hardware

**Usage**

```{r gps_plots}
gps_plots(gps, freq)
```

**Arguments**
* gps: the 3rd data frame from the load_data() function
* freq: the time interval of summary

**Value**

A list of the following plots:

1. altitude
2. number of fixes

#### 3.2.4 export_node_channel_plots

**Description**
Export plots of node x channel data

**Usage**
```{r export_node_channel_plots}
export_node_channel_plots(plotlist=NULL, health, freq="1hour", out_path=getwd(), whichplots=c(3,2,1))

```

**Arguments**

* plotlist: allows you to pass the output of node_channel_plots() if you prefer
* health: the 2nd data frame output by the load_data() function
* freq: the time interval for which you want variables to be summarized
* out_path: where you want your plots to go
* whichplots: an index vector of the available plots

**Output**

This outputs a png for each input combination of node and channel.

#### 3.2.5 export_node_plots

**Description**

Same as above; index for the plots can be chosen from the list under the `node_plots()` description.

**Usage**

```{r export_node_plots }
export_node_plots(plotlist = NULL, health, freq, out_path=getwd(), x=2, y=3, z=1)
```

**Arguments**

to assign x, y, and z, look at the descript for `node_channel_plots()` and select those plot index in the order you want them on the page.

**Output**
This outpust a png for each input node.
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
